\section{Introduction}
A study from 2013 showed that 78.6\%\footnote{http://www.forbes.com/sites/markfidelman/2013/05/19/study-78-of-salespeople-using-social-media-outsell-their-peers/ visited: 29.6.2015} of the salesmen who use social media for their sales, outbid competitors in number of sales, who did not social media for their sales.
The study confirms that not only in everyday life but also in sales business social media is becoming increasingly important because potential new customers can be acquired there. More and more frequently employees of a company that requires a new software solution, post their need in a social media forum. He hopes that he gets proposed a wide range of information on suitable products , without having to actively take care of it. The salesman in a company that sells such a software solution can comment this post and suggest his product, if he can find the post manually.
This manual browse of any social media forum takes a long time. In one second, 41.000 posts on Facebook and 4.633 posts on Twitter will be posted~\footnote{http://blog.qmee.com/wp-content/uploads/2013/07/Qmee-Online-In-60-Seconds2.png checked : 08.07.2015}. These are only the number of publised posts on the biggest social media forums. to this even smaller forums in which posts to different categories are written have to be added. A manual search of all forums is impossible. Therefore, programs are written which search these forums and extract relevant posts.\\
Per minute 70 new domains are registered.\footnote{http://blog.qmee.com/wp-content/uploads/2013/07/Qmee-Online-In-60-Seconds2.png besucht : 08.07.2015}
If every 20 minutes a new forum is created ,every 20 minutes a new program has to be written, which can browse this new forum. For this, the forum would have to be time-consuming analyzed to understand the login and search queries. If this is done , there is a possibility that this forum does not provide meaningful data and therefore the entire time was useless invested. \\
This is precisely why a general solution is described and tested here if the manual analyzing and searching of a forum can be automated. The aim is a general statement about the relevance of this forum in terms of size and the most likely to be sold product. With this information you can decide if it's worth to create a crawler for this particular website. To automate this, it must be possible to analyze the data in the Private Web. The Private Web is part of the Deep Web , which can not be indexed by search engines because the content of the Private Web is protected by password and login.
Since the Deep Web up to 2,000 times as large as Googles' searchable Surface Web, a large proportion of the internet is lost, which could play an important role in the sales business.
In order to examine this data, restrictions such as password and login have to be solved programmatically. For this purpose, the program must automatically register and log in. After this the database size and the product specific database size can be determined if the forums is serched for product specific keywords. If the forum includes a high proportion of sales oriented posts for a corporate product, this forum can be marked as appropriate for a crawl. \\
In the section `Prerequisites` preconditions such as automated login registration are described. In the chapter `Forums relevance` searching in forums and calculating the database sizes is explained. In the chapter `Evaluation` is considered whether the thesis : `It is possible to automatically determine the relevance of a forum for the sale of a company product`, can be validated or not.
\newpage